### 2016-04-29 paper/paper.tex
basics of proof-of-stake ddoscoin

@@

>>>>

TODO: how does Peercoin make sure other mint?ers can't steal the coinstake
transaction? Is it signed by the coinstake kernel, or does the coinstake kernel
include the merkle root of transactions somehow?

@@

In order to allow the victim list to be updated dynamically, DDoSCoin uses
\emph{Proof-of-Stake} to let currency holders make small changes to the list of
acceptable victim domains. Using proof-of-stake ensures that updates are only
done by actors that already have a substantial stake in the currency, either by
purchasing it, or by previously participating in the (DoS) mining themselves.

To update the list, a currency holder ``mints'' a proof-of-stake transaction
similar to Peercoin. First, they must hold a number of coins unspent for more
than 30 days, and every second, hashes the aged transaction, a recent
stake-modifier block, and a current (seconds-resolution) timestamp. If this hash
is less than the current proof-of-stake target difficulty multiplied by the
coin-age being consumed by this transaction, then the currency holder is allowed
to make a new proof-of-stake block. Inside this block, the currency holder can
make one addition to (or one deletion from) the current victim list.
